How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-17 tse-paper/content.tex
Add log

\subsection{Methodology}
In this first overview, we therefore want to survey as broad a
population of papers, books, and other scientific publications as
possible. One challenge is that no common nomenclature has been
established yet (in fact, this is one of the goals of this
article).

@@

>>>>

\subsection{Selection Protocol}
In this first overview, we therefore want to survey as broad a
population of papers, books, and other scientific publications as
possible. One challenge is that no common nomenclature has been
established yet (in fact, this is one of the goals of this
article).

@@

\subsection{Article Classification}
%todo
